Active Learning for SAT Solver Benchmarking

### 2024-05-24 paper_jar/paper.tex
abstract

\abstract{
  Benchmarking is a crucial phase when developing algorithms.
  This also applies to solvers for the SAT (propositional satisfiability) problem.
  Benchmark selection is about choosing representative problem instances that reliably discriminate solvers based on their runtime.
  In this paper, we present a dynamic benchmark selection approach based on active learning.
  Our approach predicts the rank of a new solver among its competitors with minimum runtime and maximum rank prediction accuracy.
  We evaluated this approach on the Anniversary Track dataset from the 2022 SAT Competition.
  Our selection approach can predict the rank of a new solver after about \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of about \SI{92}{\%}. 
  We also discuss the importance of instance families in the selection process. 
  Overall, our tool provides a reliable way for solver engineers to determine a new solver's performance efficiently.
}

>>>>

\abstract{
Benchmarking is a crucial phase in the development of algorithms.
This also applies to SAT solvers for the problem of propositional satisfiability.
Benchmark selection is about choosing representative problem instances that reliably discriminate solvers based on their runtime.
In this paper, we present a dynamic benchmark selection approach based on active learning.
Our approach predicts the rank of a new solver among its competitors with minimum runtime and maximum rank prediction accuracy.
This approach was evaluated on the Anniversary Track dataset from the 2022 SAT Competition.
Our selection approach can predict the rank of a new solver after approximately \SI{10}{\%} of the time it would take to run the solver on all instances of this dataset, with a prediction accuracy of approximately \SI{92}{\%}. 
Additionally, the importance of instance families in the selection process is discussed.  
In conclusion, our tool offers a reliable method for solver engineers to assess a new solver's performance in an efficient manner.
}
